---
title: "4 subsets"
author: "Jeff"
date: "4/13/2018"
output: html_document
---
### Read in Files and Load packages
```{r first, echo=FALSE,message=FALSE}
mydir <- "/dcri/cpm/projects/pro00065513_HospitalOutcomes/EWS/STAFF/jeff/"
datadir <- "/dcri/cpm/projects/pro00065513_HospitalOutcomes/EWS/DATA/analdata"
setwd(datadir)
library(data.table)
ews = fread(input = "/dcri/cpm/projects/pro00065513_HospitalOutcomes/EWS/DATA/analdata/BinaryOutcome_6hr.csv", header = TRUE)
setwd(mydir)
source("ComputeNEWS.R")
library(tidyverse)
library(tableone)
```

### Compute NEWS for each observation
```{r,echo=FALSE,message=FALSE}
list_of_index = list(ews[,'Resp'],ews[,'SpO2'],ews[,'O2'],ews[,'Temp'],ews[,'SYS'],ews[,'Pulse'],ews[,'ConsciousnessNew'])
NEWS = ComputeNEWS(ews,list_of_index)
scored_ews = cbind(ews,NEWS)
```

### Subset ID into two group:
####  1. Who has ever had a NEWS above 7 / event
####	2. Who has never had a NEWS above 7 / event
####	3. Who has ever had a NEWS above 7 /  no event
####  4. Who has never had a NEWS above 7 / no event
```{r,echo=FALSE,message=FALSE}
### Note there are some overlapping 
H_eventID = scored_ews%>% group_by(ID)%>% summarise(MaxNEWS= max(NEWS),Event = max(Event6Hr))%>%filter(MaxNEWS>7,Event==1) %>% select(ID)
L_eventID = scored_ews%>% group_by(ID)%>% summarise(MaxNEWS= max(NEWS),Event = max(Event6Hr))%>%filter(MaxNEWS<=7,Event==1) %>% select(ID)
H_noeventID = scored_ews%>% group_by(ID)%>% summarise(MaxNEWS= max(NEWS),Event = max(Event6Hr))%>%filter(MaxNEWS>7,Event==0) %>% select(ID)
L_noeventID = scored_ews%>% group_by(ID)%>% summarise(MaxNEWS= max(NEWS),Event = max(Event6Hr))%>%filter(MaxNEWS<=7,Event==0) %>% select(ID)

```

```{r,echo=FALSE,message=FALSE}
## Check dimension
sum(nrow(H_eventID),nrow(L_eventID),nrow(H_noeventID),nrow(L_noeventID))
scored_ews %>% select(ID)%>% distinct() %>% nrow()
```
```{r,echo=FALSE,message=FALSE}
### Select ID
Highevent <- scored_ews %>% filter(ID %in% H_eventID$ID)
Lowevent <- scored_ews %>% filter(ID %in% L_eventID$ID)
HighNoevent <- scored_ews %>% filter(ID %in% H_noeventID$ID)
LowNoevent <- scored_ews %>% filter(ID %in% L_noeventID$ID)
```

### Demographics Information
#### Table one
```{r,echo=FALSE,message=FALSE}
HE.demographics = select(Highevent,ID,SEX,AGE,RACEnew)
LE.demographics = select(Lowevent,ID,SEX,AGE,RACEnew)
HN.demographics = select(HighNoevent,ID,SEX,AGE,RACEnew)
LN.demographics = select(LowNoevent,ID,SEX,AGE,RACEnew)

HE.demographics$GROUP  = "High & Event"
LE.demographics$GROUP = "Low & Event"
HN.demographics$GROUP = "High & NoEvent"
LN.demographics$GROUP = "Low & NoEvent"
HE.demographics= HE.demographics %>% group_by(ID) %>% summarise(SEX = unique(SEX), AGE = mean(AGE), RACEnew = unique(RACEnew),GROUP = unique(GROUP))
LE.demographics = LE.demographics %>% group_by(ID) %>% summarise(SEX = unique(SEX), AGE = mean(AGE), RACEnew = unique(RACEnew),GROUP = unique(GROUP))
HN.demographics= HN.demographics %>% group_by(ID) %>% summarise(SEX = unique(SEX), AGE = mean(AGE), RACEnew = unique(RACEnew),GROUP = unique(GROUP))
LN.demographics= LN.demographics %>% group_by(ID) %>% summarise(SEX = unique(SEX), AGE = mean(AGE), RACEnew = unique(RACEnew),GROUP = unique(GROUP))



demographics <- rbind(HE.demographics,LE.demographics,HN.demographics,LN.demographics)
demographics.age <- as.data.frame(table(demographics[,c('SEX','GROUP')]))
demographics.race <- as.data.frame(table(demographics[,c('RACEnew','GROUP')]))


table1 <- CreateTableOne(vars = colnames(demographics)[-c(1,ncol(demographics))],strata = "GROUP", data = demographics)
print(table1, showAllLevels = TRUE)

```
#### Plot
```{r,echo=FALSE,message=FALSE}
g<-ggplot(demographics[,c('AGE','GROUP')],aes(x= AGE,colour = GROUP ))
g+geom_density()+ggtitle(label = "Age distribution among Different group")
g1<-ggplot(demographics[,c('AGE','GROUP')],aes(y= AGE,x= GROUP ))
g1+geom_boxplot(aes(fill = GROUP))+ggtitle(label = "Age distribution among Different group")

plot.age = rbind(demographics.age %>% filter(GROUP == 'High & Event') %>% mutate(Freq = Freq/nrow(HE.demographics)),demographics.age %>% filter(GROUP == 'Low & Event') %>% mutate(Freq = Freq/nrow(LE.demographics)),demographics.age %>% filter(GROUP == 'High & NoEvent') %>% mutate(Freq = Freq/nrow(HN.demographics)),demographics.age %>% filter(GROUP == 'Low & NoEvent') %>% mutate(Freq = Freq/nrow(LN.demographics)))
plot.race = rbind(demographics.race %>% filter(GROUP == 'High & Event') %>% mutate(Freq = Freq/nrow(HE.demographics)),demographics.race %>% filter(GROUP == 'Low & Event') %>% mutate(Freq = Freq/nrow(LE.demographics)),demographics.race %>% filter(GROUP == 'High & NoEvent') %>% mutate(Freq = Freq/nrow(HN.demographics)),demographics.race %>% filter(GROUP == 'Low & NoEvent') %>% mutate(Freq = Freq/nrow(LN.demographics)))
demographics.age$Freq = round(demographics.age$Freq, digits = 2)
demographics.race$Freq = round(demographics.race$Freq, digits = 2)

g2<-ggplot(plot.age, aes(x = SEX,y = Freq))
g2+geom_bar(aes(fill = GROUP), position = 'dodge', stat = 'identity') + ggtitle(label = "Sex distribution among Different group")

g3<-ggplot(plot.race, aes(x = RACEnew,y = Freq))
g3+geom_bar(aes(fill = GROUP), position = 'dodge', stat = 'identity') + ggtitle(label = "Race distribution among Different group")



```
### Comorbidities Information
#### Table one
```{r,echo=FALSE,message=FALSE}
HE.comorbid = Highevent[,c(1,13:22)]
LE.comorbid = Lowevent[,c(1,13:22)]
HN.comorbid = HighNoevent[,c(1,13:22)]
LN.comorbid = LowNoevent[,c(1,13:22)]


HE.comorbid$GROUP  = "High & Event"
LE.comorbid$GROUP = "Low & Event"
HN.comorbid$GROUP = "High & NoEvent"
LN.comorbid$GROUP = "Low & NoEvent"

HE.comorbid = HE.comorbid %>% group_by(ID) %>% summarise(Diabetes = max(HX_DIABETES), Malignancy = max(HX_MALIGNANCY), CKD = max(HX_CKD),Copd = max(HX_COPD), MI = max(HX_MI),Stroke = max(HX_STROKE),HIV = max(HX_HIV),Postop = max(HX_POSTOP), Tarnsplant = max(HX_TRANSPLANT),Surgery =max(SURGERY),GROUP = unique(GROUP))

LE.comorbid = LE.comorbid %>% group_by(ID) %>% summarise(Diabetes = max(HX_DIABETES), Malignancy = max(HX_MALIGNANCY), CKD = max(HX_CKD),Copd = max(HX_COPD), MI = max(HX_MI),Stroke = max(HX_STROKE),HIV = max(HX_HIV),Postop = max(HX_POSTOP), Tarnsplant = max(HX_TRANSPLANT),Surgery =max(SURGERY),GROUP = unique(GROUP))

HN.comorbid = HN.comorbid %>% group_by(ID) %>% summarise(Diabetes = max(HX_DIABETES), Malignancy = max(HX_MALIGNANCY), CKD = max(HX_CKD),Copd = max(HX_COPD), MI = max(HX_MI),Stroke = max(HX_STROKE),HIV = max(HX_HIV),Postop = max(HX_POSTOP), Tarnsplant = max(HX_TRANSPLANT),Surgery =max(SURGERY),GROUP = unique(GROUP))

LN.comorbid = LN.comorbid %>% group_by(ID) %>% summarise(Diabetes = max(HX_DIABETES), Malignancy = max(HX_MALIGNANCY), CKD = max(HX_CKD),Copd = max(HX_COPD), MI = max(HX_MI),Stroke = max(HX_STROKE),HIV = max(HX_HIV),Postop = max(HX_POSTOP), Tarnsplant = max(HX_TRANSPLANT),Surgery =max(SURGERY),GROUP = unique(GROUP))

comorbid = rbind(HE.comorbid,LE.comorbid,HN.comorbid,LN.comorbid)
comorbid = as.data.frame(apply(comorbid,2,factor))

table2  = CreateTableOne( vars =  colnames(comorbid)[-c(1,ncol(comorbid))], strata = "GROUP", data = comorbid)
print(table2,showAllLevels = TRUE)
```

#### Plot
```{r,echo=FALSE,message=FALSE}
gathered_co = gather(comorbid[,-1],key ='GROUP',value = "Cormorbidies")
colnames(gathered_co) = c("Group","Cormorbidies","Count")
plot_data = as.data.frame(table(gathered_co))
plot_data = plot_data[plot_data$Count == 1,]
plot_data = rbind(plot_data %>% filter(Group == 'High & Event') %>% mutate(Freq = Freq/nrow(HE.comorbid)),plot_data %>% filter(Group == 'Low & Event') %>% mutate(Freq = Freq/nrow(LE.comorbid)),plot_data %>% filter(Group == 'High & NoEvent') %>% mutate(Freq = Freq/nrow(HN.comorbid)),plot_data %>% filter(Group == 'Low & NoEvent') %>% mutate(Freq = Freq/nrow(LN.comorbid)))

g4<- ggplot(plot_data,aes(x = Cormorbidies, y = Freq)) + geom_bar(aes(fill = Group), position = 'dodge', stat = 'identity') + ggtitle(label = "Cormorbiditties distribution among Different group")
g4+theme(
      axis.text.x  = element_text(size = 10))
```

### Length of Stay for each patient
#### Plots for Length of Stay
```{r,echo=FALSE,message=FALSE}
HE.los = select(Highevent,ID,TimeFromAdmission)
LE.los = select(Lowevent,ID,TimeFromAdmission)
HN.los = select(HighNoevent,ID,TimeFromAdmission)
LN.los = select(LowNoevent,ID,TimeFromAdmission)



HE.los  = HE.los %>% group_by(ID) %>% summarise(TimeFromAdmission = max(TimeFromAdmission))
LE.los = LE.los %>% group_by(ID) %>% summarise(TimeFromAdmission = max(TimeFromAdmission))
HN.los  = HN.los %>% group_by(ID) %>% summarise(TimeFromAdmission = max(TimeFromAdmission))
LN.los = LN.los %>% group_by(ID) %>% summarise(TimeFromAdmission = max(TimeFromAdmission))

HE.los$GROUP = "High & Event"
LE.los$GROUP = "Low & Event"
HN.los$GROUP = "High & NoEvent"
LN.los$GROUP = "Low & NoEvent"


combined_los = rbind(HE.los, LE.los, HN.los, LN.los)
Lengthstay = combined_los %>% group_by(GROUP) %>% summarise(mean = mean(TimeFromAdmission), max = max(TimeFromAdmission), min = min(TimeFromAdmission),median = median(TimeFromAdmission))
Lengthstay[,2:5] = round(Lengthstay[,2:5],digits = 3)
Lengthstay
g5<- ggplot(combined_los)
g5+geom_boxplot(aes(x=GROUP, y = TimeFromAdmission,fill = GROUP))
g5+geom_density(aes(x = TimeFromAdmission, colour = GROUP))
```
### Vitals for each patient
#### Table one
```{r,echo=FALSE,message=FALSE}
HE.vitals = select(Highevent,ID,Resp,SpO2,O2,Temp,SYS,Pulse,ConsciousnessNew)
LE.vitals = select(Lowevent,ID,Resp,SpO2,O2,Temp,SYS,Pulse,ConsciousnessNew)
HN.vitals = select(HighNoevent,ID,Resp,SpO2,O2,Temp,SYS,Pulse,ConsciousnessNew)
LN.vitals = select(LowNoevent,ID,Resp,SpO2,O2,Temp,SYS,Pulse,ConsciousnessNew)



HE.vitals$GROUP = "High & Event"
LE.vitals$GROUP = "Low & Event"
HN.vitals$GROUP = "High & NoEvent"
LN.vitals$GROUP = "Low & NoEvent"


HE.vitals$ConsciousnessNew <- factor(HE.vitals$ConsciousnessNew)
LE.vitals$ConsciousnessNew <- factor(LE.vitals$ConsciousnessNew)
HN.vitals$ConsciousnessNew <- factor(HN.vitals$ConsciousnessNew)
LN.vitals$ConsciousnessNew <- factor(LN.vitals$ConsciousnessNew)


HE.vitals = HE.vitals %>% group_by(ID) %>% summarise(MeanResp = mean(Resp),MedianResp = median(Resp),MaxResp = max(Resp),MinResp = min(Resp), MeanSpO2 = mean(SpO2),MedianSpO2 = median(SpO2),MaxSpO2 = max(SpO2),MinSpO2 = min(SpO2),MeanTemp = mean(Temp),MedianTemp = median(Temp),MaxTemp = max(Temp),MinTemp = min(Temp),MeanSYS = mean(SYS),MedianSYS = median(SYS),MaxSYS = max(SYS),MinSYS = min(SYS),MeanPulse = mean(Pulse),MedianPulse = median(Pulse),MaxPulse = max(Pulse),MinPulse = min(Pulse),O2 = max(O2),ConsciousnessNew = max(as.numeric(ConsciousnessNew)),GROUP = unique(GROUP))

LE.vitals = LE.vitals %>% group_by(ID) %>% summarise(MeanResp = mean(Resp),MedianResp = median(Resp),MaxResp = max(Resp),MinResp = min(Resp), MeanSpO2 = mean(SpO2),MedianSpO2 = median(SpO2),MaxSpO2 = max(SpO2),MinSpO2 = min(SpO2),MeanTemp = mean(Temp),MedianTemp = median(Temp),MaxTemp = max(Temp),MinTemp = min(Temp),MeanSYS = mean(SYS),MedianSYS = median(SYS),MaxSYS = max(SYS),MinSYS = min(SYS),MeanPulse = mean(Pulse),MedianPulse = median(Pulse),MaxPulse = max(Pulse),MinPulse = min(Pulse),O2 = max(O2),ConsciousnessNew = max(as.numeric(ConsciousnessNew)),GROUP = unique(GROUP))

HN.vitals = HN.vitals %>% group_by(ID) %>% summarise(MeanResp = mean(Resp),MedianResp = median(Resp),MaxResp = max(Resp),MinResp = min(Resp), MeanSpO2 = mean(SpO2),MedianSpO2 = median(SpO2),MaxSpO2 = max(SpO2),MinSpO2 = min(SpO2),MeanTemp = mean(Temp),MedianTemp = median(Temp),MaxTemp = max(Temp),MinTemp = min(Temp),MeanSYS = mean(SYS),MedianSYS = median(SYS),MaxSYS = max(SYS),MinSYS = min(SYS),MeanPulse = mean(Pulse),MedianPulse = median(Pulse),MaxPulse = max(Pulse),MinPulse = min(Pulse),O2 = max(O2),ConsciousnessNew = max(as.numeric(ConsciousnessNew)),GROUP = unique(GROUP))

LN.vitals = LN.vitals %>% group_by(ID) %>% summarise(MeanResp = mean(Resp),MedianResp = median(Resp),MaxResp = max(Resp),MinResp = min(Resp), MeanSpO2 = mean(SpO2),MedianSpO2 = median(SpO2),MaxSpO2 = max(SpO2),MinSpO2 = min(SpO2),MeanTemp = mean(Temp),MedianTemp = median(Temp),MaxTemp = max(Temp),MinTemp = min(Temp),MeanSYS = mean(SYS),MedianSYS = median(SYS),MaxSYS = max(SYS),MinSYS = min(SYS),MeanPulse = mean(Pulse),MedianPulse = median(Pulse),MaxPulse = max(Pulse),MinPulse = min(Pulse),O2 = max(O2),ConsciousnessNew = max(as.numeric(ConsciousnessNew)),GROUP = unique(GROUP))

vitals = rbind(HE.vitals, LE.vitals, HN.vitals, LN.vitals)
vitals$O2 = factor(vitals$O2)
levels(vitals$O2) = c("Never","Ever")
vitals$ConsciousnessNew = factor(vitals$ConsciousnessNew)
levels(vitals$ConsciousnessNew) = c("Alert","notAlert")
table3 = CreateTableOne(vars = colnames(vitals)[-c(1,ncol(vitals))],strata = "GROUP", data = vitals)
print(table3, showAllLevels = TRUE)
```
#### Plot for Median Vitals
```{r,echo=FALSE,message=FALSE}
g1 <- ggplot(vitals) + geom_density(aes(x = MedianPulse,colour = GROUP))+geom_vline(xintercept = c(51,90))
g1
g2 <- ggplot(vitals) + geom_density(aes(x = MedianResp,colour = GROUP))+geom_vline(xintercept = c(12,20))
g2
g3 <- ggplot(vitals) + geom_density(aes(x = MedianSpO2,colour = GROUP))+geom_vline(xintercept = 96)
g3
g4 <- ggplot(vitals) + geom_density(aes(x = MedianTemp,colour = GROUP))+geom_vline(xintercept = c(36.1,38))
g4
g5 <- ggplot(vitals) + geom_density(aes(x = MedianSYS,colour = GROUP))+geom_vline(xintercept = c(111,219))
g5



# O2 And Consciousness
plot.cons = as.data.frame(table(vitals[,c("ConsciousnessNew","GROUP")]))
plot.o2 = as.data.frame(table(vitals[,c("O2","GROUP")]))


plot.cons = rbind(plot.cons %>% filter(GROUP == 'High & Event') %>% mutate(Freq = Freq/nrow(HE.vitals)),plot.cons %>% filter(GROUP == 'Low & Event') %>% mutate(Freq = Freq/nrow(LE.vitals)),plot.cons %>% filter(GROUP == 'High & NoEvent') %>% mutate(Freq = Freq/nrow(HN.vitals)),plot.cons %>% filter(GROUP == 'Low & NoEvent') %>% mutate(Freq = Freq/nrow(LN.vitals)))


plot.o2 = rbind(plot.o2 %>% filter(GROUP == 'High & Event') %>% mutate(Freq = Freq/nrow(HE.vitals)),plot.o2 %>% filter(GROUP == 'Low & Event') %>% mutate(Freq = Freq/nrow(LE.vitals)),plot.o2 %>% filter(GROUP == 'High & NoEvent') %>% mutate(Freq = Freq/nrow(HN.vitals)),plot.o2 %>% filter(GROUP == 'Low & NoEvent') %>% mutate(Freq = Freq/nrow(LN.vitals)))
g6 <- ggplot(plot.cons,aes(x = ConsciousnessNew,y=Freq)) + geom_bar(aes(fill= GROUP),position = 'dodge',stat = "identity")
g6
g7 <- ggplot(plot.o2,aes(x = O2,y=Freq)) + geom_bar(aes(fill= GROUP),position = 'dodge',stat = "identity")
g7
```
### Labs Information
#### Table one
```{r,echo=FALSE,message=FALSE}
HE.lab = select(Highevent, ID, contains("Value"))
LE.lab = select(Lowevent, ID, contains("Value"))
HN.lab = select(HighNoevent, ID, contains("Value"))
LN.lab = select(LowNoevent, ID, contains("Value"))

select_status <- function(vec){
  if(any(vec == "High"|vec == "Low")){
    res = "Abnormal"
  }
  else {
    res = vec[length(vec)]
  }
  return(res)
}
change_level <- function(x){
 levels(x)[levels(x) %in% c("High","Low")] <- "Abnormal"
 levels(x)[levels(x) == "None"] <- "Never Ordered"
 return(x)
}

HE.lab = HE.lab %>% group_by(ID) %>% summarise_all(select_status)
LE.lab = LE.lab %>% group_by(ID) %>% summarise_all(select_status)
HN.lab = HN.lab %>% group_by(ID) %>% summarise_all(select_status)
LN.lab = LN.lab %>% group_by(ID) %>% summarise_all(select_status)

HE.lab$GROUP = "High & Event"
LE.lab$GROUP = "Low & Event"
HN.lab$GROUP = "High & NoEvent"
LN.lab$GROUP = "Low & NoEvent"
lab = rbind(HE.lab,LE.lab,HN.lab,LN.lab)

lab[,-ncol(lab)] = lapply(lab[,-ncol(lab)],change_level)
lab = lapply(lab, factor)
lab = as.data.frame(lab)
levels(lab$DdimerValue) <- c(levels(lab$Ddimer),"Normal")

table4  = CreateTableOne(vars =  colnames(lab)[-c(1,ncol(lab))], strata = "GROUP", data = lab)
print(table4,showAllLevels = TRUE)
```
#### Plots for Labs Comparing Abnormal and Normal distribution 
```{r,echo=FALSE,message=FALSE}
gathered_lab = gather(lab[,-1],key =  'GROUP',value = "Labs")
colnames(gathered_lab) = c("Group","Labs","Status")
plot_data = as.data.frame(table(gathered_lab))


s1 = plot_data%>%filter(Group == "High & Event", Status !="None")
s2 = plot_data%>%filter(Group == "Low & Event", Status !="None")
s3 = plot_data%>%filter(Group == "High & NoEvent", Status !="None")
s4 = plot_data%>%filter(Group == "Low & NoEvent", Status !="None")


s5 = plot_data%>%filter(Group == "High & Event", Status =="None")
s6 = plot_data%>%filter(Group == "Low & Event", Status =="None")
s7 = plot_data%>%filter(Group == "High & NoEvent", Status =="None")
s8 = plot_data%>%filter(Group == "Low & NoEvent", Status =="None")
### Not Robust
sumorder1 = c()
for(i in 1:30){
  sumorder1[i] = s1$Freq[i]+s1$Freq[i+30]
}

sumorder2 = c()
for(i in 1:30){
  sumorder2[i] = s2$Freq[i]+s2$Freq[i+30]
}

sumorder3 = c()
for(i in 1:30){
  sumorder3[i] = s3$Freq[i]+s3$Freq[i+30]
}

sumorder4 = c()
for(i in 1:30){
  sumorder4[i] = s4$Freq[i]+s4$Freq[i+30]
}



plot_data.1 = plot_data[plot_data$Status == "Normal",]
plot_data.1 = rbind(plot_data.1 %>% filter(Group == "High & Event") %>% mutate(Freq = Freq/sumorder1),plot_data.1 %>% filter(Group == "Low & Event") %>% mutate(Freq = Freq/sumorder2),plot_data.1 %>% filter(Group == "High & NoEvent") %>% mutate(Freq = Freq/sumorder3),plot_data.1 %>% filter(Group == "Low & NoEvent") %>% mutate(Freq = Freq/sumorder4))




g8<- ggplot(plot_data.1,aes(x = Labs, y = Freq)) + geom_bar(aes(fill = Group), position = 'dodge', stat = 'identity') + ggtitle(label = "Labs distribution among Different group(Normal)")
g8+theme(
      axis.text.x  = element_text(size = 5))


plot_data.2 = plot_data[plot_data$Status == "Abnormal",]
plot_data.2 = rbind(plot_data.2 %>% filter(Group == "High & Event") %>% mutate(Freq = Freq/sumorder1),plot_data.2 %>% filter(Group == "Low & Event") %>% mutate(Freq = Freq/sumorder2),plot_data.2 %>% filter(Group == "High & NoEvent") %>% mutate(Freq = Freq/sumorder3),plot_data.2 %>% filter(Group == "Low & NoEvent") %>% mutate(Freq = Freq/sumorder4))

g9<- ggplot(plot_data.2,aes(x = Labs, y = Freq)) + geom_bar(aes(fill = Group), position = 'dodge', stat = 'identity') + ggtitle(label = "Labs distribution among Different group(Abnormal)")
g9+theme(
      axis.text.x  = element_text(size = 5))

plot_data.3 = plot_data[plot_data$Status == "None",]
plot_data.3 = rbind(plot_data.3 %>% filter(Group == "High & Event") %>% mutate(Freq = Freq/nrow(HE.lab)),plot_data.3 %>% filter(Group == "Low & Event") %>% mutate(Freq = Freq/nrow(LE.lab)),plot_data.3 %>% filter(Group == "High & NoEvent") %>% mutate(Freq = Freq/nrow(HN.lab)),plot_data.3 %>% filter(Group == "Low & NoEvent") %>% mutate(Freq = Freq/nrow(LN.lab)))
g10<- ggplot(plot_data.3,aes(x = Labs, y = Freq)) + geom_bar(aes(fill = Group), position = 'dodge', stat = 'identity') + ggtitle(label = "Labs distribution among Different group(None)")
g10+theme(
      axis.text.x  = element_text(size = 5))

```
#### Tables for Labs Comparing "High","Low","Normal" Rate
```{r Lab table , echo=FALSE,message=FALSE,warning=FALSE}
HE.lab1 = select(Highevent, ID, contains("Value"))
LE.lab1 = select(Lowevent, ID, contains("Value"))
HN.lab1 = select(HighNoevent, ID, contains("Value"))
LN.lab1 = select(LowNoevent, ID, contains("Value"))

HE.lab1$GROUP = "High & Event"
LE.lab1$GROUP = "Low & Event"
HN.lab1$GROUP = "High & NoEvent"
LN.lab1$GROUP = "Low & NoEvent"

lab1 = rbind(HE.lab1, LE.lab1,HN.lab1,LN.lab1)

simplefun<-function(x){x[length(x)]}
lastorder <-lab1 %>% group_by(ID) %>% summarise_all(simplefun)
simplefun2<-function(x){
  kk = x %>% filter(x[,1]!="None")
  kk[,1]<-factor(unlist(kk[,1]))
  res = prop.table(table(kk),margin = 2)
  chi = chisq.test(table(kk))
  return(list(res,chi))
  }


res = list()
k=1
for(i in colnames(lastorder)[-c(1,ncol(lastorder))]){
  a1 = simplefun2(lastorder[,c(i,"GROUP")])[[1]]
  a2 = simplefun2(lastorder[,c(i,"GROUP")])[[2]]$p.value
  res[[k]] = list(round(a1,2),round(a2,2))
  k=k+1
} 
res
```

### Medication for each patient
#### Table One
```{r medication, echo=FALSE,message=FALSE}
medi <- fread(input ="/cpm/projects/pro00065513_HospitalOutcomes/EWS/DATA/rawdata/DUH/tbl_med_2#6#17.txt" )


Highevent$Group = "High & Event"
Lowevent$Group = "Low & Event"
HighNoevent$Group = "High & NoEvent"
LowNoevent$Group = "Low & NoEvent"

gevent = rbind(Highevent, Lowevent, HighNoevent, LowNoevent)
med.event <- gevent[gevent$ID %in% medi$PAT_ENC_CSN_ID,]

cromedi<-filter(medi,PAT_ENC_CSN_ID %in% med.event$ID)
theclass<- select(cromedi,PAT_ENC_CSN_ID, THERA_CLASS)
theclass$value = 1
tc <- theclass %>% group_by(PAT_ENC_CSN_ID) %>% distinct() %>% spread(key = THERA_CLASS,value = value) %>% mutate_all(funs(replace(.,is.na(.),0)))

new.tc = tc %>% arrange(PAT_ENC_CSN_ID)
class(new.tc)<-"data.frame"
new.tc = cbind(new.tc, med.event %>% group_by(ID) %>% summarise(Group = unique(Group)) %>% arrange(ID) %>% select(Group))
new.tc= apply(new.tc,2,factor)
new.tc = as.data.frame(new.tc)
colnames(new.tc)[7] <-"PSYCHOTHERAPEUTIC_DRUGS"
table5  = CreateTableOne( vars =  colnames(new.tc)[-c(1,ncol(new.tc))], strata = "Group", data = new.tc)
print(table5, showAllLevels = TRUE)


```
#### Plots for Medication
```{r med plots, echo=FALSE,message=FALSE}
gathered_med = gather(new.tc[,-1],key =  'Group',value = "Medication")
colnames(gathered_med) = c("Group","Medication","Count")
plot_data_med = as.data.frame(table(gathered_med))
plot_data_med = plot_data_med[plot_data_med$Count == 1,]
plot_data_med = rbind(plot_data_med %>% filter(Group == "High & Event") %>% mutate(Freq = Freq/nrow(new.tc%>%filter(Group == "High & Event"))),plot_data_med %>% filter(Group == "Low & Event") %>% mutate(Freq = Freq/nrow(new.tc%>%filter(Group =="Low & Event"))),plot_data_med %>% filter(Group == "High & NoEvent") %>% mutate(Freq = Freq/nrow(new.tc%>%filter(Group == "High & NoEvent"))),plot_data_med %>% filter(Group == "Low & NoEvent") %>% mutate(Freq = Freq/nrow(new.tc%>%filter(Group =="Low & NoEvent"))))

g11<- ggplot(plot_data_med,aes(x = Medication, y = Freq)) + geom_bar(aes(fill = Group), position = 'dodge', stat = 'identity') + ggtitle(label = "Medication distribution among Different group")
g11+theme(
      axis.text.x  = element_text(size = 7))

```

